---
title: "HwkGLM"
format: html
editor: visual
---

## Model Hawk GLM

This is an attempt to build code for a generalize linear model. The data used are predator-prey reaction behaviors collected by launching a model hawk at birds in the Amazon in Madre de Dios, Peru. Reactions include: no response, call, alarm, sing, dive, hide, freeze, visual search

### Installing Packages

```{r}
#install.packages("glmm")

library(glmm)
library(here)
library(tidyverse)

```

## Loading Hawk Data

```{r}
hwk_data <- read_csv(here("data/hwkGLM.csv"))
tibble(hwk_data)

```

## Generalized Linear Model 1 (larger index)

```{r}
model <- glm(Mid_Join_Index1 ~ Mid_Join, data = hwk_data, family = poisson(link = "log"))
model
```

## Generalized Linear Model 2 (conservative)

```{r}
model <- glm(Mid_Join_Index2 ~ Social_Index + SpeciesID + Pre_Height + Pre_Dense, data = hwk_data, family = poisson(link = "log"))
summary(model)
```

response \~ species + veg density + foraging + sociality

Sociality: MSF, singles, pairs, leks, SSF (single species group)
